Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-07 WSSSPE3/report/wg_main_user_community.tex
edits & suggestions in user community section

\subsection{Building Sustainable User Communities for Scientific Software}
%\todo{change the title to your topic}

\subsubsection{Why it is important}
%\todo{short text here}

@@

\subsubsection{Fit with related activities}
%\todo{short text here - can include links/cites}

Mozilla Science maintains a ``Working Open' Project Guide'' (http://mozillascience.github.io/leadership-training). From the introduction:
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}

Several books have been written about software communities:
\begin{itemize}
\item ``Art of Community'' by Jono Bacon. We could consider distilling this for scientific software.
\item Iain Larmour, from EPSRC inthe UK (EPSRC: https://www.epsrc.ac.uk/) (not sure who from mentioned UK Collaborative Computational Projects (CCP: http://ccp.ac.uk)
\end{itemize}

\subsubsection{Discussion}
%\todo{short-ish text here}

@@

In describing best practices, the group discussed the different modes for starting a scientific software project: building on
an existing product that needs improving, recognizing an unsatisfied need of an existing community, or creating a new solution
to a need not yet recognized by the community. The group also thought that the existing books on software communities would
need to be evaluated in light of differences between Science Software projets and general OSS projects in terms of scale,
science, acknowledgement and credit, and funding models.

\subsubsection{Plans}
%\todo{short text here - not bullets}

>>>>

\subsection{Building Sustainable User Communities for Scientific Software}

%\subsubsection{Why it is important}

@@

\subsubsection{Fit with related activities}

Mozilla Science maintains a ``Working Open Project Guide'' (\url{http://mozillascience.github.io/leadership-training}). \katznote{should get changed to a cite} From the introduction:
\begin{quote}
Working openly with contributors enables your
    community to learn how to build and collaborate together. This
    document is a guideline on how to work openly and involve others
    in your projects with Mozilla. We want to help you engage your
    community in a way that encourages contributors and builds other
    leaders.
 \end{quote}

Several books have been written about software communities:
\begin{itemize}
\item ``Art of Community'' by Jono Bacon. \katznote{cite?} We could consider distilling this for scientific software.
\item Iain Larmour, from EPSRC in the UK (EPSRC: https://www.epsrc.ac.uk/) (not sure who from mentioned UK Collaborative Computational Projects (CCP: http://ccp.ac.uk)
\end{itemize}

\subsubsection{Discussion}

@@

In describing best practices, the group discussed the different modes for starting a scientific software project: building on
an existing product that needs improving, recognizing an unsatisfied need of an existing community, or creating a new solution
to a need not yet recognized by the community. The group also thought that the existing books on software communities would
need to be evaluated in light of differences between Science Software projects and general OSS projects in terms of scale,
science, acknowledgement and credit, and funding models.

Additional details on the group's discussion can be found in Appendix~\ref{sec:appendix_user_community}.

\subsubsection{Plans}
